---
title: "Project_part3"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(tidy.opts = list(width.cutoff = 60), tidy = TRUE)
library(lmtest)
library(forecast)
library(vars)
library(tseries)
```


```{r}
# Get the data
setwd("/Users/minchenwang/classes/604/project")
df1 <- read.csv("train.csv", header=T)
df2 <- read.csv("test.csv", header=T)
full_ts <- ts(df1$Bankruptcy_Rate, frequency = 12)
```

As Adam did, split the last three years for the test data.
```{r}
n_months <- 36
train <- ts(df1$Bankruptcy_Rate[1:(nrow(df1)- n_months)], frequency = 12)
test <- ts(df1$Bankruptcy_Rate[(nrow(df1)- n_months + 1):nrow(df1)],
frequency = 12, start = nrow(df1)/12 - n_months/12 +1)
plot(train, xlim = c(1,29))
lines(test, col = 'blue')
```

# Auto Arima Model

Use Box-Jenkins Methodology to do the data transformation
```{r}
lambda <- BoxCox.lambda(train)
train_trans <- (train^lambda-1)/lambda
```

Check how many time differences is necessary
```{r}
print(ndiffs(train_trans))
print(ndiffs(train_trans,m=12))
```

```{r}
# differencing once
dtrain_trans <- diff(train_trans)
# differencing for monthly seasonality
dtrain_trans.12 <- diff(dtrain_trans, lag=12)
# check the stationary
adf.test(dtrain_trans.12)
```
```{r}
plot(dtrain_trans.12)
```

Find auto.arima() recommendation for the seires
```{r}
m.aut <- auto.arima(y = train_trans, d = 1, D = 1, allowdrift = F)
summary(m.aut)
```

Draw the auto-arima forecast plot
```{r}
m <- arima(train_trans, order=c(2,1,3), seasonal = list(order = c(2,1,2), period = 12), method="CSS-ML")
fit <- ((train_trans - m$residuals)*lambda + 1)^(1/lambda)
plot(train, type = "l", main = "Bankruptcy Rate", xlim=c(0,28),ylim=c(0,6))
t1 <- time(train)
points(t1, fit, type = "l", col = "red")
f.aut <- forecast(object = m, h = 36, level = 0.95)
point <- ((f.aut$mean)*lambda + 1)^(1/lambda)
lower <- ((f.aut$lower)*lambda + 1)^(1/lambda)
upper <- ((f.aut$upper)*lambda + 1)^(1/lambda)
abline(v=26,col='blue',lty=2)
t2 <- time(test)
polygon(c(t2, rev(t2)), c(upper, rev(lower)), col = "grey90", border = NA)
points(point~t2, type='l', col='red')
points(test[1:36]~t2, type='l', col='black')
legend("topleft", legend = c("Observed", "Predicted", "Interval"),
       lty = 1, lwd = c(1,1,10), col = c("black", "red", "grey90"), cex = 1)
```


auto-arima RMSE
```{r}
accuracy(f.aut,test)
```

RMSE = 2.01684849
\newpage

## Holt-Winters Methodology

```{r}
m.hw <- HoltWinters(x = train, seasonal = "multi")
m.hw
```

Draw the Holt-Winters forecast plot
```{r}
f.hw <- forecast(m.hw, h = 36, level = 0.95)
plot(train, type = "l", main = "Bankruptcy Rate", xlim=c(0,28),ylim=c(0,6))
lines(m.hw$fitted[,1], col = "red", lwd = 1.5)
t1 <- time(train)
point <- f.hw$mean
lower <- f.hw$lower
upper <- f.hw$upper
abline(v=26,col='blue',lty=2)
t2 <- time(test)
polygon(c(t2, rev(t2)), c(upper, rev(lower)), col = "grey90", border = NA)
points(point~t2, type='l', col='red')
points(test[1:36]~t2, type='l', col='black')
legend("topleft", legend = c("Observed", "Predicted", "Interval"),
       lty = 1, lwd = c(1,1,10), col = c("black", "red", "grey90"), cex = 1)
```

??? I don't know why the interval exploded into so large after 27.

Holt-Winters RMSE
```{r}
accuracy(f.hw,test)
```
The Holt-Winters RMSE=0.3006421 looks good.
